Scheduling and Vectorization for MPC

### 2022-03-01 paper_SIMD.tex
Minor edits to Array section.

\COMMENT { Phase 3: Dimensionality reduction: removing unnecessary dimensionality. }

@@

Note however, that this step renders some array phi-nodes target-less. We handle target-less phi-nodes with a minor extension of Basic Vectorization. 
First, we merge closures that update the same array. \ana{Why, intuition?} Second, we add the target-less node of array \texttt{A} back to the closure that updates \texttt{A} ---
the intuition is, even if there is no loop-carried dependence from writes to reads on \texttt{A}, \texttt{A} is written and the write (i.e., update) cannot be vectorized; 
therefore, the updated array has to carry to the next iteration of the loop. Third, in cases when the phi-node remains target-less, i.e., cases when the
array write can be vectorized, we have to properly remove the phi-node replacing uses of the left-hand side of the phi-node with its arguments.

>>>>

\COMMENT { Phase 3: Remove unnecessary dimensionality. }

@@

Note however, that this step renders some array phi-nodes target-less. We handle target-less phi-nodes with a minor extension of Basic Vectorization. 
First, we merge closures that update the same array. This simplifies handling of array $\phi$-nodes: if each closure is turned into a separate loop
each loop will need to have its own array phi-node to account for the update and this would complicate the analysis.
Second, we add the target-less node of array \texttt{A} back to the closure that updates \texttt{A} ---
the intuition is, even if there is no loop-carried dependence from writes to reads on \texttt{A}, \texttt{A} is written and the write (i.e., update) cannot be vectorized; 
therefore, the updated array has to carry to the next iteration of the loop. Third, in cases when the phi-node remains target-less, i.e., cases when the
array write can be vectorized, we have to properly remove the phi-node replacing uses of the left-hand side of the phi-node with its arguments.
